Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2021-01-11 submission/NatCom_cv_models.tex
updated tablesd

\michael{Charles, any more sentences to add to the last three paragraphs to clarify anything?  If not, then just comment out this comment.}
\charles{In partcular, the PL-based AlphaHat $\hat{\alpha}$ and Shatten-Norm $\langle\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ metrics 
tend to perform better when there is a wider variation in the hyper-parameters going beyond just increasing the depth.  In fact sometimes the
purely norm-based metrics such as the Spectral Norm can be uncorrelated or even
anti-correlated with the test accuracy, as seen in Section~\ref{} with
ShuffleNet in Figure~\ref{fig:summary_regressions_B_02},
SqueezeNext in Figure~\ref{fig:summary_regressions_C_10},
and WRN in Figure~\ref{fig:summary_regressions_G_06}).
}

>>>>

\michael{Charles, any more sentences to add to the last three paragraphs to clarify anything?  If not, then just comment out this comment.}
\charles{In partcular, the PL-based AlphaHat $\hat{\alpha}$ and Shatten-Norm $\langle\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ metrics 
tend to perform better when there is a wider variation in the hyper-parameters going beyond just increasing the depth.  In fact sometimes the
purely norm-based metrics such as the Spectral Norm can be uncorrelated or even
anti-correlated with the test accuracy, where the PL-metrrics are positively-correlated.
This is seen in Section~\ref{sxn:appendix} with
ShuffleNet in Figure~\ref{fig:summary_regressions_B_02},
SqueezeNext in Figure~\ref{fig:summary_regressions_C_10},
and WRN in Figure~\ref{fig:summary_regressions_G_06}).}
